%%% LaTeX Template: Curriculum Vitae
%%%
%%% Source: http://www.howtotex.com/
%%% Feel free to distribute this template, but please keep the referal to HowToTeX.com.
%%% Date: July 2011

%%% ------------------------------------------------------------
%%% BEGIN PREAMBLE
%%% ------------------------------------------------------------
\documentclass[paper=a4,fontsize=11pt]{scrartcl}	 			% KOMA-article class

%\usepackage[english]{babel}								% English language/hyphenation
%\usepackage[protrusion=true,expansion=true]{microtype}		% Better typography
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amsthm}					% Math packages
\usepackage[pdftex]{graphicx}								% Enable pdflatex
\usepackage[svgnames]{xcolor}							% Colors by their 'svgnames'
\usepackage{geometry}
	\textheight=700px									% Saving trees ;-)
\usepackage{url}										% Clickable URL's
\usepackage{wrapfig}									% Wrap text along figures

\frenchspacing									% Better looking spacings after periods
\pagestyle{empty}								% No pagenumbers/headers/footers
%\usepackage{bbding}									% Symbols

%%% Custom sectioning (sectsty package)
%%% ------------------------------------------------------------
\usepackage{sectsty}							% Custom sectioning (see below)

\sectionfont{%									% Change font of \section command
  \usefont{OT1}{phv}{b}{n}%					% bch-b-n: CharterBT-Bold font
  \sectionrule{0pt}{0pt}{-5pt}{3pt}
	}

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{888888888888}				% Box to align text
\newcommand{\sepspace}{\vspace*{1em}}			% Vertical space macro

\newcommand{\MyName}[1]{
		\Huge \usefont{OT1}{phv}{b}{n} \hfill #1 		% Name
		\par \normalsize \normalfont}

\newcommand{\MySlogan}[1]{
		\large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1} % Slogan (optional)
		\par \normalsize \normalfont}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
		\noindent\hangindent=2em\hangafter=0 		% Indentation
		\parbox{\spacebox}{						% Box to align text
		\textit{#1}}								% Entry name (birth, address, etc.)
		\hspace{1.5em} #2 \par}					% Entry value

\newcommand{\SkillsEntry}[2]{						% Same as \PersonalEntry
		\noindent\hangindent=2em\hangafter=0 		% Indentation
		\parbox{\spacebox}{						% Box to align text
		\textit{#1}}								% Entry name (birth, address, etc.)
		\hspace{1.5em} #2 \par}					% Entry value

\newcommand{\EducationEntry}[4]{
		\noindent \textbf{#1} \par 					% Study
		\noindent \textit{#3} \hfill					% School
		\colorbox{Black}{%
			\hfill\color{White}#2} \par				% Duration
		\noindent\hangindent=2em\hangafter=0 \small #4 	% Description
		\normalsize \par
    }

\newcommand{\ReferenceEntry}[1]{
        \large
		\noindent \textbf{#1} \par
		\normalsize \par
    }

\newcommand{\WorkEntry}[4]{					        % Same as \EducationEntry
		\noindent \textbf{#1} \hfill 				% Jobname
		\colorbox{Black}{\color{White}#2} \par		% Duration
		\noindent \textit{#3} \par					% Company
		\noindent\hangindent=2em\hangafter=0 \small #4 	% Description
		\normalsize \par}

\newcommand{\ProjectEntry}[4]{
		\noindent \textbf{#1} \hfill 	        	% Jobname
		\colorbox{Black}{\color{White}#2} \par		% Duration
		\noindent\hangindent=2em\hangafter=0 \small #3 	% Description
		\normalsize \par \sepspace}



%%% ------------------------------------------------------------
%%% BEGIN DOCUMENT
%%% ------------------------------------------------------------
\begin{document}

\MyName{Attila Nagy}
%\MySlogan{Curriculum Vitae}

%%% Personal details
%%% ------------------------------------------------------------
\NewPart{Contact}{}

\PersonalEntry{Phone}{+46 708499543}
\PersonalEntry{Mail}{attilanagy85@gmail.com}
\PersonalEntry{GitHub}{https://github.com/NagyAttila}
%\PersonalEntry{HomePage}{https://nagyattila.tech}

\NewPart{Introduction}{}

I have a background in telecommunication, automotive industry and machine learning. In the recent years I have developed an interest in deep learning through self-studies, that led to my previous job at RumbleStrip. We worked on adaptive spoilers for the heavy truck industry to lower fuel consumption. Before that, I worked with self-driving cars at Volvo Cars in Active-Safety, and with 3G networks at Nokia Siemens Networks in Budapest. Currently I am working on PacketCore at Ericsson.

My technical interest mostly rotates around open-source software development, cryptography, Linux, machine and deep learning, functional programming, and a little bit of web-development. In my working environment, I tend to be social and discuss books and podcasts I read and listened recently.

My current greatest endeavour is to start my own company and work as a free-lancer.

  %Most of my personal life I like to spend in nature doing sports like climbing, yoga, running, hiking and camping. When the winters are too rough on me, I like to indulge myself in board game nights and old science fiction movies from the 50's. Furthermore, I have great interest in culinary pleasures. As one of my hobbies, I build a thermostat box to be able experiment with different food fermentation methods. One of my success stories is tempeh from chickpeas, and currently focusing on fermentation with lentils and rice. As a final interest, I have good stories from my travels in Southeast Asia involving rocket launchers in Cambodia, acrobatics with monkeys in Indonesia, finding skeleton remains in a cave on The Philippines, and many more.

%%% Work
%%% ------------------------------------------------------------
\NewPart{Work}{}

\WorkEntry{HiQ, Consultant at Ericsson}{04/2020 -- Now}{Software Developer, Sweden, Full-time}

\SkillsEntry{Roles:}{Functional Tester, System Tester, DevOps}

\SkillsEntry{Programming:}{C++, TTCN}

\SkillsEntry{Applications:}{LTE, PacketCore}

%\SkillsEntry{Principles:}{Scrum, Agile}

\sepspace

\WorkEntry{RumbleStrip}{09/2017 -- 10/2019}{Software Architect and Developer, Sweden, Full-time}

\SkillsEntry{Roles:}{SW Architect, Algorithm Developer}

\SkillsEntry{Programming:}{Python, C, Matlab}

\SkillsEntry{Applications:}{Adaptive Roof-Deflector, Data-Analysis}

%\SkillsEntry{Principles:}{Scrum, Agile}

\sepspace

\WorkEntry{ÅF, Consultant at Volvo Cars}{07/2014 -- 07/2016}{Self-Driving Car Engineering, Sweden, Full-time}

\SkillsEntry{Roles:}{Self-Driving Car Developer, Unit Tester}

\SkillsEntry{Programming:}{Matlab, Simulink, Python, C++}

\SkillsEntry{Applications:}{Active-Safety, Data-Analysis, Sensor-Fusion, Mapping, Logging}

%\SkillsEntry{Principles:}{Scrum, Agile}

\sepspace

\WorkEntry{Nokia Siemens Networks}{08/2009 -- 08/2012}{Software Engineer, Hungary, Full-time}

\SkillsEntry{Roles:}{Scrum Master, Functional Tester, Unit Tester, DevOps}

\SkillsEntry{Programming:}{C/C++, Python, Perl, BASH, TNSDL, LDAP}

%\SkillsEntry{Testing:}{CxxTest, testAnt, Jenkins}

\SkillsEntry{Debugging:}{GDB, Valgrind, oProfile}

%\SkillsEntry{Principles:}{Scrum, Agile, TDD}

\clearpage

%%%% Education
%%%% ------------------------------------------------------------
\NewPart{Education}{}

\EducationEntry{Deep Learning Nanodegree}{01/2017 -- 06/2017}
{Udacity, www.udacity.com} {Assigment 1: Vanilla Neural Network from scratch\\
 Assigment 2: Image Classification by Convolutional Neural Network\\
 Assigment 3: TV script generation by Recurrent Neural Network\\
 Assigment 4: Language-translation by Recurrent Neural Network\\
 Assigment 5: Face image generation by Generative Adversarial Networks \\
 Source-code: https://github.com/NagyAttila/Udacity\_DLND\_Assigments \\
 %Syllabus: https://www.udacity.com/course/deep-learning-nanodegree--nd101
 }
\sepspace

\EducationEntry{MSc. Computer Science}{09/2012 -- 04/2014}
  {Chalmers University of Technology, Sweden}{Specialization: Distributed Systems and Networks\\
  Thesis' Title: Energy Efficient, High-speed Communication in Wireless Sensor Networks\\
  Thesis' Keywords: Opportunistic Routing, Bulk-transfer, TinyOS, nesC\\
  Student Project: Carolo Cup, Germany, self-driving miniature cars, team leader\\
  Research Project: Power consumtion disaggregation and clsassification with SVM}
\sepspace

\EducationEntry{ERASMUS Scholarship}{09/2008 -- 01/2009}
{University of Applied Sciences Ravensburg-Weingarten, Germany}
{Field: Embedded Systems }
\sepspace

\EducationEntry{BSc. Electrical Engineering}{09/2004 -- 06/2009}{Obuda University, Hungary}{Specialization: Embedded Systems\\
Thesis' Title: Robot Simulation isepspacenGL Environment\\
Thesis' Keywords: Industrial robot simulation, OpenGL, C++. \\
Student Project: Remote-controlled miniature car via bluetooth, 8-bit Atmega micro-controller}

\NewPart{Languages}{}
\SkillsEntry{ }{English}
\SkillsEntry{}{Swedish}
\SkillsEntry{}{Hungarian}

\NewPart{Interest}{}
\SkillsEntry{Technical:}{machine learning}
\SkillsEntry{}{free/open-source software}
\SkillsEntry{}{blockchain technology}
\SkillsEntry{}{functional programming}

\sepspace
\SkillsEntry{Sports:}{rock climbing}
\SkillsEntry{}{slacklining}
\SkillsEntry{}{running}
\SkillsEntry{}{yoga}

\sepspace
\SkillsEntry{Others:}{meditation}
\SkillsEntry{}{politics}

\clearpage

\NewPart{Projects}{}

\ProjectEntry{HiQ, Consultant at Ericsson}{04/2020 -- Now}
{
    After 10 years I am back in Telecom working on the next generation of telecommunication networks. Most of my work
    currently involves development on the PacketCore network, Functional Testing using TTCN and System Tests.
}

\ProjectEntry{RumbleStrip}{09/2017 -- 10/2019}
{
    Working with adaptive roof-deflectors for trucks using machine learning, AWS and embedded systems to lower fuel
    consumption.  Mostly worked with a Bayesian Regression model for predicting the optimal position of the roof-
    deflector.  But earlier at the proof of concept stage we experimented with a variant of K-Nearest- Neighbour
    algorithm, Decision Trees and Deep Neural Networks.  At the end due to the lack of available data and limitations in
    our product's HW, we decided to use a Bayesian Regression model.  Sensor data was collected using Python on a
    RaspberryPi, stored in AWS, and evaluated in Matlab.  Later, our model was prototyped in an embedded environment on
    a STM32 board, and field tested using LINAK-LA32 actuators on Volvo trucks.
}

\ProjectEntry{ÅF, Consultant at Volvo Cars}{07/2014 -- 07/2016}
{
    I worked as a SW developer in Active Safety in the Sensor Fusion team using Matlab and Simulink.  My work mostly
    involved post-processing of sensory data for our particle filter algorithm, that fused our positions from the GPS
    sensor and the IMU.
}

\ProjectEntry{Nokia Siemens Networks}{08/2009 -- 08/2012}
{
    As part of the HLR and DXA teams for 3G development, I worked in a cross-functional team, doing testing, coding and
    maintenance using C++ and Python.
}

\NewPart{References}{}
\ReferenceEntry{Milad Pouyanmehr}{}{}
\SkillsEntry{Phone:}{+46 767607403}
\SkillsEntry{Email:}{milad@rumblestrip.tech}
\SkillsEntry{From:}{RumbleStrip}
\sepspace

\ReferenceEntry{David Andersson}{}{}
\SkillsEntry{Phone:}{+46 735803819}
\SkillsEntry{Email:}{david.andersson@nvidia.com}
\SkillsEntry{From:}{Volvo Cars Corporation}

% \ReferenceEntry{Joakim Lin-S\"orstedt}
% \SkillsEntry{Phone:}{+46 723716181}
% \SkillsEntry{Email:}{jaokim.lin-sorstedt@zenuity.com}
% \SkillsEntry{From:}{Volvo Cars Corporation}
% \sepspace

\end{document}
